\EVOSUITE at the SBFT 2023 Tool Competition

### 2023-03-10 papers/sbst23/paper_sbst23.tex
Small pass over competition setup

The 2022 competition setup was identical to the 2021 setup: The most recent
version of \EVOSUITE (1.1.0) was used, which by default uses
DynaMOSA~\cite{dynamosa} as the search algorithm. No new features were added in
this version, but support for Java 9+ was added, several bugs were fixed, and a
major refactoring was applied to improve the code quality with respect to the
use of Java Generics internally. While several smaller bugfixes were applied in
the run-up to the 2021 competition, no further optimisation or testing was
applied for 2022.

The configuration is largely identical to the established configuration used in
prior years, and mainly uses the tuned default
values~\cite{arcuri2013parameter} and default coverage criteria
\cite{rojas2015combining}.
%
As in previous years, the configuration omits the test minimisation step as the
competition score does not reward test minimality, and the minimisation takes
substantial computational effort. Similarly, the configuration includes all
regression assertions rather than filtering them with mutation analysis to save
time.
%
The time budget was again distributed by allocating \SI{50}{\percent} of the overall time
set by the competition organisers for the search, and the other \SI{50}{\percent} equally to
the remaining phases (e.g., assertion generation, compile-check,
flakiness-check).

>>>>

The 2023 competition setup was similar to the 2022 setup: The same version of
\EVOSUITE (1.1.0) was used, which by default uses DynaMOSA~\cite{dynamosa} as
the search algorithm.
% No new features were added in this version, but support
% for Java 9+ was added, several bugs were fixed, and amajor refactoring was applied
% to improve the code quality with respect to the
% use of Java Generics internally. While several smaller bugfixes were applied in
% the run-up to the 2021 competition, no further optimisation or testing was
% applied for 2022.

The configuration is largely identical to the established configuration used in
prior years, and mainly uses the tuned default
values~\cite{arcuri2013parameter} and default coverage criteria
\cite{rojas2015combining}.
%
Unlike previous years, where the competition score did not yet reward readability,
the configuration now enables a test minimisation step, and filters regression
assertions using mutation analysis.
%
The time budget was again distributed by allocating \SI{50}{\percent} of the overall time
set by the competition organisers for the search, and the other \SI{50}{\percent} equally to
the remaining phases (e.g., assertion generation, compile-check, flakiness-check).
